---
title: "Mini-Project 1: Text Analysis"
---



# Mini-Project 1: Text Analysis

## Introduction

For Mini-Project 1, I analyzed immigration-related tweets. Social media platforms like Twitter are important places where people express opinions about immigration, refugees, asylum, borders, and migration.

The goal of this project was to identify common themes, word patterns, and emotional tone in the tweets.

## Data

The dataset includes a random sample of immigration-related tweets. I cleaned the tweet text by changing it to lowercase, removing links, and identifying migration-related words.

## Methods

I used text analysis tools in R, including `stringr`, `tidytext`, and sentiment analysis. I used regular expressions to remove links and identify words related to immigration, refugees, migrants, asylum, and borders.

## Results

### Most Common Words

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(stringr)
library(tidytext)

tweets <- readr::read_csv("https://raw.githubusercontent.com/jmrphy/migration_tweets/master/cleaned_data/random_sample.csv")

tweets_clean <- tweets |>
  mutate(
    text_lower = str_to_lower(text),
    text_nolink = str_replace_all(text_lower, "http\\S+", "")
  )

tweet_words <- tweets_clean |>
  select(text_nolink) |>
  unnest_tokens(word, text_nolink) |>
  anti_join(stop_words, by = "word")

common_words <- tweet_words |>
  count(word, sort = TRUE)

common_words |>
  slice_max(n, n = 10) |>
  ggplot(aes(x = reorder(word, n), y = n)) +
  geom_bar(stat = "identity") +
  coord_flip()
```

This plot shows the most common words in the tweets. Words such as “immigration,” “uk,” and “immigrants” appear frequently.

### Sentiment Analysis

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tweet_sentiment <- tweet_words |>
  inner_join(get_sentiments("bing"), by = "word")

tweet_sentiment |>
  count(sentiment) |>
  ggplot(aes(x = sentiment, y = n)) +
  geom_bar(stat = "identity")
```
This plot shows that negative words appear more often than positive words.

### Most Common Sentiment Words
```{r, echo=FALSE, message=FALSE, warning=FALSE}
top_sentiment_words <- tweet_sentiment |>
  count(word, sentiment, sort = TRUE) |>
  group_by(sentiment) |>
  slice_max(n, n = 10)

ggplot(top_sentiment_words, aes(x = reorder(word, n), y = n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  facet_wrap(~sentiment) +
  coord_flip()
```
This plot shows the most common positive and negative words in the tweets.

## Conclusion

Overall, this project shows that text analysis can help reveal patterns in social media discussions about immigration. The tweets often included strong opinions, and negative language appeared more frequently than positive language. However, some positive language related to reform and support was also present.