---
title: "Mini-Project 1: Text Analysis"
---


## Introduction

For Mini-Project 1, I analyzed immigration-related tweets. Social media platforms like Twitter are important places where people express opinions about immigration, refugees, asylum, borders, and migration.

The goal of this project was to identify common themes, word patterns, and emotional tone in the tweets.

## Data

The dataset includes a random sample of immigration-related tweets. I cleaned the tweet text by changing it to lowercase, removing links, and identifying migration-related words.

## Methods

I used text analysis tools in R, including `stringr`, `tidytext`, and sentiment analysis. I used regular expressions to remove links and identify words related to immigration, refugees, migrants, asylum, and borders.

## Results

### Most Common Words

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(stringr)
library(tidytext)

tweets <- readr::read_csv("https://raw.githubusercontent.com/jmrphy/migration_tweets/master/cleaned_data/random_sample.csv")

tweets_clean <- tweets |>
  mutate(
    text_lower = str_to_lower(text),
    text_nolink = str_replace_all(text_lower, "http\\S+", "")
  )

tweet_words <- tweets_clean |>
  select(text_nolink) |>
  unnest_tokens(word, text_nolink) |>
  anti_join(stop_words, by = "word")

common_words <- tweet_words |>
  count(word, sort = TRUE)

common_words |>
  slice_max(n, n = 10) |>
  ggplot(aes(x = reorder(word, n), y = n)) +
  geom_bar(stat = "identity") +
  coord_flip()
```

This plot shows the most frequent words used in immigration-related tweets. Terms like “immigration,” “uk,” and “immigrants” appear most often, suggesting that the discussion is focused on policy and national debates. The presence of words like “illegal” also indicates that the conversation may include controversial or sensitive topics.

### Sentiment Analysis

```{r, echo=FALSE, message=FALSE, warning=FALSE}
tweet_sentiment <- tweet_words |>
  inner_join(get_sentiments("bing"), by = "word")

tweet_sentiment |>
  count(sentiment) |>
  ggplot(aes(x = sentiment, y = n)) +
  geom_bar(stat = "identity")
```
This plot compares the number of positive and negative words in the tweets. Negative words appear much more frequently than positive ones, indicating that discussions about immigration tend to be more critical or emotionally charged. This suggests that immigration is often discussed in a negative or concerned tone on social media.

### Most Common Sentiment Words
```{r, echo=FALSE, message=FALSE, warning=FALSE}
top_sentiment_words <- tweet_sentiment |>
  count(word, sentiment, sort = TRUE) |>
  group_by(sentiment) |>
  slice_max(n, n = 10)

ggplot(top_sentiment_words, aes(x = reorder(word, n), y = n, fill = sentiment)) +
  geom_bar(stat = "identity") +
  facet_wrap(~sentiment) +
  coord_flip()
```
This plot shows the most common positive and negative words used in the tweets. Negative words such as “illegal,” “fears,” and “racist” appear frequently, highlighting the intensity of negative sentiment. At the same time, positive words like “support” and “reform” also appear, suggesting that some tweets focus on solutions or advocacy. Overall, the discussion includes both criticism and support.

## Conclusion

Overall, this project shows that text analysis can help reveal patterns in social media discussions about immigration. The tweets often included strong opinions, and negative language appeared more frequently than positive language. However, some positive language related to reform and support was also present.